Hysteresis in human computation:\\ how one task affects another

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
updates to figure legends

\paragraph{Detailed influences on worker outputs.} 
\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
	\caption{
		Detailed exposure effects on workers' label vocabulary, for various
		exposure modalities and prime concepts (see Table 1).  A) Change in 
		the number of food-related labels used. B) Change in the total number 
		of \textit{unique} food-related labels used. C) Relative specificity
		of treatment pairs, when considering food-related labels.  For all
		plots, a positive bar height indicates an increase for the 
		food-exposed treatment for the pair indicated on the abscissa.
	}
	\label{fig:specificity}
\end{figure}

>>>>

\paragraph{Detailed influences on worker outputs.} 
\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
	\caption{
		Intertask and framing effects on the vocabulary workers use to refer 
		to food(\#), when labeling images, for various treatment pairs.
		A) Relative change in the number references to food. 
		B) Relative change in the number of \textit{unique} 
		references to food (lexical richness). 
		C) Relative specialization of food references, based on the 
		hypernym-hyponym relations (this calculation is shown in the 
		supplementary text).  For all
		plots, a positive bar height indicates that the \textit{*:food}
		treatment has more of the quantity than its conjugate treatment.
	}
	\label{fig:specificity}
\end{figure}
